\documentclass[11pt]{article}

\iffalse

\fi

\begin{document}
    \begin{titlepage}
    \title {Proof of Concept Demonstration                     Plan}
    \maketitle
        \begin{center}
		SE 2XA3\\
		\author{
		Hui Chen\hspace{128pt}chenh43	
		\\*Nareshkumar Maheshkumar\hspace{35pt}maheshn 
		\\*Sam Hamel\hspace{118pt}hamels2 \\
		}
		\end{center}
    \end{titlepage}
    
    \newpage
      We will be demonstrating a prototype of the game where there will be two players instead of one player  versus a computer, and where a dummy procedure will be used to determine which poker hand wins. All other functionality needed in the final version will be present in the proof of concept. The proof of concept will not have a graphical user interface and will instead be using a text interface. 
 	\subsection*{Identify the Most Significant Risks}
    The most significant risks are time constraints, proving the correctness and effectiveness of the product and testing the graphical user interface.
    \subsection*{Will a part of the implementation be difficult?}
	The graphical interface component of the implementation will be difficult to implement as the graphical interface requires the backend components in order to display that component on the interface. Card strength and AI will be difficult to implement as there are many ways to evaluate hand strength and to build an AI. Therefore picking the appropriate method and integrating it with the product will be difficult. 

    \subsection*{Will testing be difficult?}
    The graphical user interface will be difficult to test since the only way to test it is to play the game, which may prove incomprehensive and the results will prove inadequate . The results also vary based on the individual games as the algorithm used to deal cards is random. Testing for the other components of the product will not be difficult and will be done through JUnit and individual unit tests for each of the classes. Junit will be used to test each and every method, object and class within the product. 

    \subsection*{Is a required library difficult to install?}
    Only built in standard Java libraries are used for this project, so there is no need to install other libraries. 

    \subsection*{Will portability be a concern?}
    Portability will not be a concern because the product be able to run on any machine that has Java installed. 
    \subsection*{Will the project size/scope be
              feasible?}
	The project size/scope will be feasible if the proof of concept is feasible because most components of the product will be included in the proof of concept, and the remaining tasks will be feasible once the proof of concept is completed. 
  

\end{document}

